---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.align="center"
)
library(rjd3x13)
```

# rjd3x13

rjd3x13 offers full acces to options and outputs of X-13 (`rjd3x13::x13()`), including RegARIMA modelling (`rjd3x13::regarima()`) and X-11 decomposition (`rjd3x13::x11()`).

The specification can be created with the functions `rjd3x13::spec_regarima()`, `rjd3x13::spec_x11()` or `rjd3x13::spec_x13()` and can be modified with the function:

- for the pre-processing: `rjd3toolkit::set_arima()`, `rjd3toolkit::set_automodel()`, `rjd3toolkit::set_basic()`, `rjd3toolkit::set_easter()`, `rjd3toolkit::set_estimate()`, `rjd3toolkit::set_outlier()`, `rjd3toolkit::set_tradingdays()`, `rjd3toolkit::set_transform()`, `rjd3toolkit::add_outlier()`, `rjd3toolkit::remove_outlier()`, `rjd3toolkit::add_ramp()`, `rjd3toolkit::remove_ramp()`, `rjd3toolkit::add_usrdefvar()`;

- for the decomposition: `rjd3x13::set_x11()`;

- for the benchmarking: `rjd3toolkit::set_benchmarking()`.
 

## Installation


```{r, eval = FALSE}
# Install development version from GitHub
# install.packages("remotes")
remotes::install_github("rjdemetra/rjd3toolkit")
remotes::install_github("rjdemetra/rjd3x13")
```

## Usage

```{r x-13-final}
library(rjd3x13)
y <- rjd3toolkit::ABS$X0.2.09.10.M
x13_model <- x13(y) 
summary(x13_model$result$preprocessing) # Summary of regarima model
plot(x13_model) # Plot of the final decomposition
```

To get the final components you can use the function `rjd3toolkit::sa_decomposition()`:

```{r x-13-fin-comp}
rjd3toolkit::sa_decomposition(x13_model)
```
